 

### 2021-05-04 vertical-thermal-review.Rmd
Update vertical-thermal-review.Rmd

>>>>

*from Martijn in Tleaves figure: One thing that might be more relevant in tropical than in seasonal temperate forests, is the issue I mentioned before about the difference between shade leaves of canopy trees and leaves of understory species. The understory species in the tropics (the ones that won't necessarily make it to the canopy, and can reproduce in the understory) appear to invest more in leaf longevity than in light harvesting per se, so even though they are in the shade, they do not have large leaves with low LMA. This would be a deviation on, or a special case of, the understory parameters you are using now. I don't think we necessarily need to incorporate that in this figure, but I think it would be useful to be able to say that for understory species with small, high LMA leaves the effects of windspeed, radiation, RH, etc, are greater/smaller than for the understory species parameters in the figure. DOes this make sense? Is this relevant at all for seasonal forests? The only thing that comes to mind is Ilex, but maybe there are other species?*
